Structured Versus Decorated Cospans

### 2020-12-10 cospans.tex
fixed remark at end of Section 2

This theorem should generalize to the case when $\theta$ is a pseudonatural
isomorphism, but the weaker version suffices for our application in \cref{subsec:petrirates}.

>>>>

This theorem should generalize to the case when $\theta$ is a pseudonatural equivalence, but the weaker version suffices for our application in \cref{subsec:petrirates}.
